---
title: "Exploring cats and their habits"
author: "Mine Çetinkaya-Rundel"
format: 
  html:
    toc: true
editor: visual
---

## Data

Because I'm a cat lover...

## Packages

In this analysis I'll use the **tidyverse** package for data wrangling and visualization, the **scales** package for better axis labels, and the **janitor** package for cleaning variable names.

```{r}
#| label: load-packages
#| message: false

library(tidyverse)
library(scales)
library(janitor)
# add other packages, if any
```

## Explorations

In this project I'll be exploring why some cats like catnip as well as why some don't like being petted.

```{r}
# label: load-data
# message: false

#cats <- read_csv("some tidytuesday URL")
```

### Why do cats like catnip?

Update title (try to keep it short) and add narrative and code...

### Why don't some cats like being petted?

Update title (try to keep it short) and add narrative and code...

(Add more explorations as needed, or take this out.)

## Discussion

Summary of findings on the data and what you learned in the process about the data context as well as about using R.
